### 2019-08-30 Writeup/Thesis/chapters/design.tex
Changes; - All fixes implemented from supervisor feedback
Changes; - Re-drafted after reading over a printed version

The attack on Trustwords involves generating "near-collision" keys. 
This attempts to provide the base to answer Research Questions \ref{goal:numberOfTrustwords} and \ref{goal:complexity}.

@@

When attacking a similarity metric is used to compute a list of possibilities for each position in the target fingerprint.

@@

\subsection{Metaphone}
Metaphone as discussed in Section \ref{sec:metaphone} is anther famous phonetic algorithm. Metaphone is arguably on the same level of ubiquity as that of Soundex with it finding itself implemented in languages such as PHP\cite{php}. Metaphone was chosen due to similar reasons to that of Soundex and NYSIIS.

Further work would involve the implementation of newer versions of Metaphone. Double Metaphone (2000) and
Metaphone 3 (2009) that claim to improve over the original version due to further research performed by Philips.

@@

The design for the experiment involves assessing the quality of the metrics matches by having participants rate them on a scale of 1 to 5.

@@

\todo{Link the less than 100,000 point to experiment data}

@@

The first consideration is the way the words are compared. Due to the channel of authentication being phone-based, the comparison of words is a mixture of auditory and textual. This mixture is because a user needs to match a words sound to the one displayed on their device. This experiment asks users to compare the sound of two words that are visually displayed to them. This visual aspect is the first point of contact between the participant and the question, followed by a mental comparison of the phonetics of the word. Therefore, this initial visual contact has the potential to bias the results of the study. Levenshtein has the potential to be most affected by this due to the matches never being more than one character different, therefore, resulting in very similar-looking words. The alternative method of running this experiment is to get users to compare audio samples of words; this forces the user to compare just the phonetics of the words and not be influenced by the visual aspects of the pair. However, this adds a substantial cost to the operation of the study. Due to the aforementioned lack of resources, the chosen design was decided as most feasible as it is a balance between cost and accuracy. Further work, therefore, could improve by producing more conclusive results on the performance of the metrics by implementing the more accurate but costly alternative.

@@

Appendix \ref{appendix:trustword_attack} shows the design of the experiments front end\footnote{A live version can also be viewed at the url: \url{https://afray.pythonanywhere.com/}}. As can be seen by comparing it to Figure \ref{fig:trustwords}, it has been designed to be as close as possible to the actual application. The blue button is clicked to simulate the authentication ceremony over the phone. A text-to-speech system then read a set of words and the user should accept if they match and decline if they don't.

@@

Due to the scarcity of attacks in a real-world setting, users are often complacent about their occurrence. Therefore, in this experiment, attacks only occur 30\% of the time. This occurrence is a much higher value than in a real-world setting, but is a balance between resources and realistic design. If the chosen attack rate is too low, many more trials are required to collate a useful number of attack instances, thus, requiring more resources but with a much more realistic design. If, however, the attack rate is too high, less total rounds are required to obtain the target number of attack trails, however, the user will lose their complacency as an attack will be expected. This loss of complacency is undesirable as it does not realistically reflect real life. Furthermore, the first 5 trials of a new experiment is always benign. This inclusion is to ensure users are consistently lulled into of complacency.

@@

Audio-buttons-clicks is the number of times the blue \textit{"Authenticate with partner over the phone"} button in Figure \ref{fig:expID} is clicked. If there are rounds without button clicks, this is a sign of non-attentiveness. The design choice was made to keep this as a result filter, as preventing non-clicks would be a trivial task. This design provides a way to detect and discard click-throughs\footnote{Workers that aim to complete the task as fast as possible, with no regard for the quality of responses}.

>>>>

The attack on Trustwords involves generating "near-collision" keys. 
This attempts to provide the base to answer Research Questions \ref{goal:complexity} and \ref{goal:numberOfTrustwords}.

@@

When attacking, a similarity metric is used to compute a list of possibilities for each position in the target fingerprint.

@@

\subsection{Metaphone}
Metaphone as discussed in Section \ref{sec:metaphone} is another famous phonetic algorithm. Metaphone is arguably on the same level of ubiquity as that of Soundex with it finding itself implemented in languages such as PHP\cite{php}. Metaphone was chosen due to similar reasons to that of Soundex and NYSIIS.

Further work would involve the implementation of newer versions of Metaphone. Double Metaphone (2000) and
Metaphone 3 (2009) that claim to improve over the original version.

@@

The design for the experiment involves assessing the quality of the metrics matches by having participants rate them on a scale of 1 (Very different sound) to 5 (Very similar sound).

@@

@@

The first consideration is the way the words are compared. Due to the assumed context of authentication being phone-based, the comparison of words is a mixture of auditory and visual. The user will hear their authentication partner read their set of words (Auditory) and compare to their set of words (Visual). This mixture is because a user needs to match a words sound to the one displayed on their device. This experiment asks users to compare the sound of two words that are visually displayed to them. This visual aspect is the first point of contact between the participant and the question, followed by a mental comparison of the phonetics of the word. Therefore, this initial visual contact has the potential to bias the results of the study. Levenshtein has the potential to be most affected by this due to the matches never being more than one character different, therefore, resulting in very similar-looking words. The alternative method of running this experiment is to get users to compare audio samples of words; this forces the user to compare just the phonetics of the words and not be influenced by the visual aspects of the pair. However, this adds a substantial cost to the operation of the study. Due to the aforementioned lack of resources, the chosen design was decided as most feasible as it is a balance between cost and accuracy. Further work, therefore, could improve by producing more conclusive results on the performance of the metrics by implementing the more accurate but costly alternative.

@@

Appendix \ref{appendix:trustword_attack} shows the design of the experiments front end\footnote{A live version can also be viewed at the url: \url{https://afray.pythonanywhere.com/}}. As can be seen by comparing it to Figure \ref{fig:trustwords}, it has been designed to be as close as possible to the actual application. The blue button is clicked to simulate the authentication ceremony over the phone. A text-to-speech system then reads a set of words and the user should accept if they match and decline if they don't.

@@

Due to the scarcity of attacks in a real-world setting, users are often complacent about their occurrence. Therefore, in this experiment, attacks only occur 30\% of the time. This occurrence is a much higher value than in a real-world setting, but is a balance between resources and realistic design. If the chosen attack rate is too low, many more trials are required to collate a useful number of attack instances, thus, requiring more resources, but with more realism. If, however, the attack rate is too high, less total rounds are required to obtain the target number of attack trails, however, the user will lose their complacency as an attack will be expected. This loss of complacency is undesirable as it does not realistically reflect real life. Furthermore, the first 5 trials of a new experiment is always benign. This inclusion is to ensure users are consistently lulled into of complacency.

@@

Audio-buttons-clicks is the number of times the blue \textit{"Authenticate with partner over the phone"} button in Figure \ref{fig:expID} is clicked. If there are rounds without button clicks, this is a sign of non-attentiveness. The design choice was made to allow non-clicks as an attention check. This design provides a way to detect and discard click-throughs\footnote{Workers that aim to complete the task as fast as possible, with no regard for the quality of responses}.

### 2019-08-30 Writeup/Thesis/chapters/evaluation.tex
Changes; - Re-drafted after reading over a printed version

Research Question 1 asks: \textit{“What are the best performing schemes to quantify phonetic similarity?”}. This paper has discussed several metrics used to quantify phonetic similarity (See Section \ref{sec:metrics}). Most metrics were chosen due to their high utilization and occurrence in literature. The only exception to this is the presence of Phonetic Vectors that were chosen due to their unique qualities. Performance of these metrics were then quantified in a direct study that selected the top three from a set of five (See Section \ref{exp:metric}). These newly selected metrics were then assessed in an attack context with their performance being indirectly quantified (See Section \ref{sec:exp2_design}).

@@

\section{Research Question \ref{goal:complexity}}
Research Question \ref{goal:complexity}: \textit{``What are the time and computation complexity required to generate a ’similar’ keys for a targeted key pair?''} has been discussed by the project, the actual generation of keys as shown in Section \ref{sec:key_gen} where actual keys were generated. Furthermore, the distribution of key permutations on a set of real-world keys were discussed in Section \ref{sec:averagePerms} and \ref{sec:vulnKeys}. To achieve this, the tool GreenOnion was developed where inspiration was gathered from a currently available tool known as Scallion. Experimentation results were gathered and displayed in Section \ref{sec:SvG} that showed the significant increase in the number of near-collision keys GreenOnion can test for with GreenOnion being able to handle in excess of 1.5 million keys. This capability is in comparison to the maximum of 2513 keys Scallion can compare. We believe this is due to the implementation of the bloom filter. Its unique characteristics of $O(k)$ complexity regardless of number of elements in the structure allows a huge number of concurrent checks to occur.

@@

Furthermore, comparison of these results to similar literature shows a considerable increase in success rates for the attack present in this paper. We believe this is due to the consideration of `similarity' when forming attacks. This was an aspect missing from the literature.
The effect of `similarity' is further enhanced due to the  weaknesses present in Trustwords such as homophones, dual mappings and the wordlist size. Therefore, we believe that 4 Trustwords as a minimum has not provided a basic level of security towards users.

@@

\subsection*{Trustword improvements}
The first area of proposed work could be recommendations into how to improve Trustwords backed by empirical evidence. We feel the most promising avenue would be the utilization of Phonetic Vectors unique qualities to identify words of low quality by measuring very low vector distances. For example, present in the dictionary are the words \verb|THERE| and \verb|THEIR|, these could be massively improved upon and could result in a better quality word list. Moreover, utilizing the quantification of dissimilarity could be used to create a dictionary of maximized phonetic distance that could then be assessed in a similar way to detect the feasibility of the attack with the alterations and its success rate against users.

>>>>

Research Question 1 asks: \textit{“What are the best performing schemes to quantify phonetic similarity?”}. This paper has discussed several metrics used to quantify phonetic similarity (See Section \ref{sec:metrics}). Most metrics were chosen due to their high utilization and occurrence in literature. The only exception to this is the presence of Phonetic Vectors. Performance of these metrics were then quantified in a direct study that selected the top three from a set of five (See Section \ref{exp:metric}). These newly selected metrics were then assessed in an attack context with their performance being indirectly quantified (See Section \ref{sec:exp2_design}).

@@

\section{Research Question \ref{goal:complexity}}
Research Question \ref{goal:complexity}: \textit{``What are the time and computation complexity required to generate a ’similar’ keys for a targeted key pair?''} has been discussed by the project, the actual generation of keys as shown in Section \ref{sec:key_gen}. Furthermore, the distribution of key permutations on a set of real-world keys were discussed in Section \ref{sec:averagePerms} and \ref{sec:vulnKeys}. To achieve this, the tool GreenOnion was developed. Inspiration for GreenOnion was gathered from a currently available tool known as Scallion. Experimentation results were gathered and displayed in Section \ref{sec:SvG} that showed the significant increase in the number of near-collision keys GreenOnion can test for with GreenOnion being able to handle in excess of 1.5 million keys. This capability is in comparison to the maximum of 2513 keys Scallion can compare. We believe this is due to the implementation of the bloom filter. Its unique characteristics of $O(k)$ complexity regardless of number of elements in the structure allows a huge number of concurrent checks to occur.

@@

Furthermore, comparison of these results to similar literature shows a considerable increase in success rates for the attack present in this paper. We believe this is due to the consideration of `similarity' when forming attacks. This was an aspect missing from the literature.
We also believe the effect of considering similarity is further enhanced due to the  weaknesses present in Trustwords such as homophones, dual mappings and the wordlist size. Therefore, we believe that four Trustwords as a minimum has not provided a basic level of security towards users.

@@

\subsection*{Trustword improvements}
The first area of proposed work could be recommendations into how to improve Trustwords backed by empirical evidence. We feel the most promising avenue would be the utilization of Phonetic Vectors unique qualities to identify words of low quality by measuring very low vector distances. For example, present in the dictionary are the words \verb|THERE| and \verb|THEIR|, these could be massively improved upon and could result in a better quality word list. Moreover, utilizing the quantification of dissimilarity could be used to create a dictionary of maximized phonetic distance. This phonetically distinct wordlist could then be assessed in a similar with its success rate quantified against users.

### 2019-08-30 Writeup/Thesis/chapters/experiments.tex
Changes; - Re-drafted after reading over a printed version

Table \ref{tab:exp1_demo} contains the demographical breakdown of the reduced set of participants. The average ages of the participants were 37.3 years ($\sigma = 11.67$)with a split of 44.4\% of Males to 55.6\% of Females. As can be seen, over 60\% of participants can be considered highly educated (Bachelor’s and up). This level of education is not sufficiently reflective of the general population and therefore, has to be considered when interpreting the results. All participants were sourced from the US; this again requires consideration due to the broad range of dialects present that may bias the results. Further work could investigate the effect of location and dialect on similar results.

@@

Figure \ref{tab:exp1_results} shows the average results for the selected matches explained in Section \ref{sec:exp1_comparison}. It can be seen that Levenshtein came out substantially above the rest. The breakdown of the ratings in Figure \ref{fig:exp1_breakdown} also shows Levenshtein's dominance. Levenshtein has a much more significant proportion of 4 and 5 ratings than the alternatives. This performance may, however, be due to the visual way the comparisons are being performed. (Discussed in detail in Section \ref{sec:exp1_considerations}).

@@

The reduced set of 369 participants had an average age of 36.63 ($\sigma = 11.35$) and consisted of an almost equal split of Male (50.41\%) to Female (49.59\%). Around 62\% of participants had completed a single stage of university (Bachelor and up). This aspect makes this set of participants more educated than the general population. All participants were also sourced from the USA and have rated themselves as fully native English speakers.
\begin{table}[!h]
    \centering
    \begin{tabular}{|l|l|}
        \hline
        Browser & Percentage \\
        \hline
        Chrome & 85.1\% \\
        Firefox & 12.2\% \\
        Safari & ~~1.9\% \\
        Other & ~~0.8\% \\
        \hline
    \end{tabular}
    \caption{Internet Browser breakdown}
    \label{tab:exp2_browser}
    \begin{tabular}{|l|l|}
        \hline
        Operating System & Percentage \\
        \hline

@@

\subsection*{Results}
Table \ref{tab:exp2_attacks} contains the break down of results for the experiment. It can be seen that the best metric out of the set was Levenshtein with an overall success of 19.80\%. The best performer, when regarding attack strength, as expected, is the 2 static words. Levenshtein's 2 static attack performed the best overall with a success rate of 32.05\%. The worst performer was Metaphone, with an average of 16.88\% over its three levels of attacks. When comparing the performance of the metrics to the previous experiment the ordering remains the same with Levenshtein, NYSIIS and Metaphone all ranking in the same order.

\begin{table}
    \makebox[\textwidth][c]{
        \centering
        \begin{tabular}{|ll|l|l|l|}
            \hline
            \textbf{Metric} & & \textbf{Successful Attacks} & \textbf{Total Attacks} & \textbf{Success Rate} \\
            \hline
            Levenshtein && 218 & 1101 & 19.8\% \\
            \hline
            & 0 static   & 34  & 358  & ~~9.5\% \\
            & 1 static   & 59  & 353  & 16.7\% \\
            & 2 static   & 125  & 390  & 32.1\% \\
            \hline\hline
            Metaphone &&  181 & 1072 & 16.9\% \\
            \hline
            & 0 static   & 38 & 345 & 11.0\% \\
            & 1 static   & 57 & 375 & 15.2\% \\
            & 2 static   & 86 & 352 & 24.4\% \\
            \hline\hline
            NYSIIS &&  209 & 1114 & 18.8\% \\
            \hline
            & 0 static   & 36 & 385 & ~~9.3\% \\
            & 1 static   & 72 & 375 & 19.2\% \\
            & 2 static   & 101 & 354 & 28.5\% \\
            \hline\hline
            \textbf{Overall} & & 608 & 3287 & 18.5\% \\
            \hline\hline
        \end{tabular}
    }
    \caption{Success rates for simulated attacks}
    \label{tab:exp2_attacks}
\end{table}

\subsection*{Considerations}
As previously mentioned, the set of recruited participants are more highly educated than the general population. This. combined with the lower average age, contributes to an inevitable bias being introduced into the data. An assumption can be made that higher education leads to more skilful interaction with computer-based systems, this, therefore, with the previous assumption in mind means the results of this experiment can be considered a `best case' scenario. The attacks, therefore, would be expected to be more successful on less technical users. This consideration, however, requires further research and possible empirical data to determine the validity of the assumption.

@@

Other relevant work by \textbf{Dechand \textit{el al.}}\cite{dechand2016empirical} also discussed in Chapter \ref{cha:LiteratureReview} assess the success rate of attacks on words. Their experiment is less similar as 14 words per attack were assessed with each participant, where the comparison was performed visually. However, the success was 8.78\%. As 10/14 words were kept static, this result is more comparable to the highest attack strength ``2 static''. This, therefore, leads to another 3 fold improvement in the success rates of our simulated attacks.

@@

\begin{table}[!h]
    \makebox[\textwidth][c]{
        \centering
        \begin{tabular}{|llll|}
            \hline
            \textbf{Metric} & & \textbf{Mean matches} & \textbf{Compute Time} \\
            \hline
            NYSIIS &&& \\
            \hline
            & 0 static & 1963.07 &  ~~27.19 days \\
            & 1 static & 448.37 &  119.14 days \\
            & 2 static & 98.07 &  ~~~~1.49 years \\
            \hline\hline

            Metaphone &&& \\
            \hline
            & 0 static & 27138.78 &  ~~~~1.97 days \\
            & 1 static & 2822.74 &  ~~18.91 days \\
            & 2 static & 339.84 &  157.45 days \\
            \hline\hline

            Levenshtein &&& \\
            \hline
            & 0 static & 293.92 &  182.17 days \\
            & 1 static & 102.75 &  ~~~~1.43 years \\
            & 2 static & 35.53 &   ~~~~4.18 years \\
            \hline\hline

@@

        \begin{tabular}{|lll|}
            \hline
            \textbf{Attack Type} & \textbf{Metric} & \textbf{Vulnerable \%} \\
            \hline 
            2 static (152) && \\ 
            & Levenshtein & ~~4.295\% \\
            & Metaphone & 24.095\% \\
            & NYSIIS & 10.441\% \\
            \hline\hline
            1 static (1525) && \\ 
            & Levenshtein & ~~0.827\% \\
            & Metaphone & 15.569\% \\
            & NYSIIS & ~~4.341\% \\
            \hline\hline
            0 static (15250) && \\ 
            & Levenshtein & ~~0.157\% \\
            & Metaphone & 10.202\% \\
            & NYSIIS & ~~1.824\% \\
            \hline\hline
        \end{tabular}
    }
    \caption{Number of vulnerable keys per metric}
    \label{tab:vulnkeys}
\end{table}

Table \ref{tab:vulnkeys} contains the breakdown of the number of vulnerable keys. The takeaways from this table are the extremely low values for Levenshtein in the higher attacks. This phenomenon is due to the low number of overall matches produced by Levenshtein, meaning Levenshtein is effective in the vast majority of cases. However, the standout metric is Metaphone with a sizeable proportion of vulnerable keys; it was the worst performer when assessed against real users but only by as little as 2\%. If you take into consideration, the number of vulnerable keys detected in the set alongside the average amount of near-collision matches in Table \ref{tab:average_perm} Metaphone appears to be the most usable metric overall.

\section{Generation of keys}
\label{sec:key_gen}
In order to demonstrate that the generation of the near-collision keys is not only theoretical, the actual generation of keys was performed using GreenOnion. A random metric was selected from the three carried forward from the first experiment. Alongside this, a random uncontrolled key was generated as the simulated attack target (See Appendix \ref{appendix:uncontrolled_key} for the armor public key). Then for each attack level (0 static, 1 static, 2 static), a key was computed. NYSIIS was chosen as the selected metric. To expedite the process, an initial search was performed for controlled keys that had the highest number of near-collisions; this was due to the demonstrative purpose of this experiment. Producing near-matching keys from key pairs with a very small number of potential matches adds very little to this demonstration. This, however, will result in best-case scenario key computation times.

@@

    \makebox[\textwidth][c]{
        \begin{tabular}{|l|l|}
            \hline
            Potential near-collision keys & 142,296 \\
            Hashing speed & 4000 MH/s \\
            Estimated computation time & 9 hours \\
            Actual computation & 6.41 hours \\
            GPU Days & 0.52 \\
            \hline
            Original Trustwords & BELL GRIND ALGERIA ANNULI \\
            Actual Trustwords   & BOIL GRAND ALGER ANNUL \\
            \hline
        \end{tabular}
    }
    \caption{NYSIIS - 0 static}
    \label{tab:nysiis0}

    \makebox[\textwidth][c]{    
        \begin{tabular}{|l|l|}
            \hline
            Potential near-collision keys & 133,200 \\
            Hashing speed & 8000 MH/s \\
            Estimated computation time & 4.2 hours \\
            Actual computation & 5.12 hours \\
            GPU Days & 0.853 \\
            \hline
            Original Trustwords & ASSUMING SONOMA DENS KEENER \\
            Actual Trustwords   & ASSUMING SUMMON DENNI CONNOR \\
            \hline
        \end{tabular}
    }
    \caption{NYSIIS - 1 static}
    \label{tab:nysiis1}

    \makebox[\textwidth][c]{
        \begin{tabular}{|l|l|}
            \hline
            Potential near-collision keys & 16,464 \\
            Hashing speed & 6000 MH/s \\
            Estimated computation time & 2.16 days \\
            Actual computation & 23.44 hours \\
            GPU Days & 2.93 \\
            \hline
            Original Trustwords & VOCATION BORE TANN ANTE \\
            Actual Trustwords   & VOCATION BARE TONE ANTE \\
            \hline
        \end{tabular}
    }
    \caption{NYSIIS - 2 static}
    \label{tab:nysiis2}
\end{table}

@@

As can be seen most notably from Table \ref{tab:nysiis2}, the generation of the actual Trustwords differs in only 3 characters making it arguably very similar. When linking this generated key to results of the second experiment (See Section \ref{sec:exp2}) computation of 2.53 days on a single mid-range GPU can achieve around a 28\% success rate when assessed against actual users. Even with the least restricted attack type presented in Table \ref{tab:nysiis0}, the computation of half a day can provide almost a 10\% success rate when attacking users. This results in any user with a single commodity GPU could compute enough keys in less than a week to have a very high probability of fooling an actual user.

>>>>

Table \ref{tab:exp1_demo} contains the demographical breakdown of the reduced set of participants. The average ages of the participants were 37.3 years ($\sigma = 11.67$) with a split of 44.4\% of Males to 55.6\% of Females. As can be seen, over 60\% of participants can be considered highly educated (Bachelor’s and up). This level of education is not sufficiently reflective of the general population and therefore, has to be considered when interpreting the results. All participants were sourced from the US; this again requires consideration due to the broad range of dialects present that may bias the results. Further work could investigate the effect of location and dialect on similar results.

@@

Figure \ref{tab:exp1_results} shows the average results for the selected matches explained in Section \ref{sec:exp1_comparison}. It can be seen that Levenshtein came out substantially above the rest. The breakdown of the ratings in Figure \ref{fig:exp1_breakdown} also shows Levenshtein's dominance. Levenshtein has a much more significant proportion of 4 and 5 ratings than the alternatives. This performance may, however, be due to the visual way the comparisons are performed. (Discussed in detail in Section \ref{sec:exp1_considerations}).

@@

The reduced set of 369 participants had an average age of 36.63 ($\sigma = 11.35$) and consisted of an almost equal split of Male (50.4\%) to Female (49.6\%). Around 62\% of participants had completed a single stage of university (Bachelor and up). This aspect makes this set of participants more educated than the general population. All participants were also sourced from the USA and have rated themselves as fully native English speakers.
\begin{table}[!h]
    \centering
    \begin{tabular}{|l|l|}
        \hline
        Browser & Percentage \\
        \hline
        Chrome & 85.1\% \\
        Firefox & 12.2\% \\
        Safari & ~~1.9\% \\
        Other & ~~0.8\% \\
        \hline
    \end{tabular}
    \caption{Internet Browser breakdown}
    \label{tab:exp2_browser}
    \begin{tabular}{|l|l|}
        \hline
        Operating System & Percentage \\
        \hline

@@

\subsection*{Results}
Table \ref{tab:exp2_attacks} contains the break down of results for the experiment. It can be seen that the best metric out of the set was Levenshtein with an overall success of 19.80\%. The best performer, when regarding attack strength, as expected, is the \XOOX~attack. Levenshtein's \XOOX~attack performed the best overall with a success rate of 32.05\%. The worst performer was Metaphone, with an average of 16.88\% over its three levels of attacks. When comparing the performance of the metrics to the previous experiment the ordering remains the same with Levenshtein, NYSIIS and Metaphone all ranking in the same order.

\begin{table}
    \makebox[\textwidth][c]{
        \centering
        \begin{tabular}{|ll|l|l|l|}
            \hline
            \textbf{Metric} & & \textbf{Successful Attacks} & \textbf{Total Attacks} & \textbf{Success Rate} \\
            \hline
            Levenshtein && 218 & 1101 & 19.8\% \\
            \hline
            & \OOOO   & 34  & 358  & ~~9.5\% \\
            & \XOOO   & 59  & 353  & 16.7\% \\
            & \XOOX   & 125  & 390  & 32.1\% \\
            \hline\hline
            Metaphone &&  181 & 1072 & 16.9\% \\
            \hline
            & \OOOO   & 38 & 345 & 11.0\% \\
            & \XOOO   & 57 & 375 & 15.2\% \\
            & \XOOX   & 86 & 352 & 24.4\% \\
            \hline\hline
            NYSIIS &&  209 & 1114 & 18.8\% \\
            \hline
            & \OOOO   & 36 & 385 & ~~9.3\% \\
            & \XOOO   & 72 & 375 & 19.2\% \\
            & \XOOX   & 101 & 354 & 28.5\% \\
            \hline\hline
            \textbf{Overall} & & 608 & 3287 & 18.5\% \\
            \hline\hline
        \end{tabular}
    }
    \caption{Success rates for simulated attacks}
    \label{tab:exp2_attacks}
\end{table}

\subsection*{Considerations}
As previously mentioned, the set of recruited participants are more highly educated than the general population. This combined with the lower average age, contributes to an inevitable bias being introduced into the data. An assumption can be made that higher education leads to more skilful interaction with computer-based systems, this, therefore, with the previous assumption in mind means the results of this experiment can be considered a `best case' scenario. The attacks, therefore, would be expected to be more successful on less technical users. This consideration, however, requires further research and possible empirical data to determine the validity of the assumption.

@@

Other relevant work by \textbf{S. Dechand \textit{el al.}}\cite{dechand2016empirical} also discussed in Chapter \ref{cha:LiteratureReview} assess the success rate of attacks on words. Their experiment is less similar as 14 words per attack were assessed with each participant, where the comparison was performed visually. However, the success was 8.78\%. As 10/14 words were kept static, this result is more comparable to the highest attack strength ``2 static''. This, therefore, leads to another 3 fold improvement in the success rates of our simulated attacks.

@@

\begin{table}[!h]
    \makebox[\textwidth][c]{
        \centering
        \begin{tabular}{|llll|}
            \hline
            \textbf{Metric} & & \textbf{Mean matches} & \textbf{Compute Time} \\
            \hline
            NYSIIS &&& \\
            \hline
            & \OOOO & 1963.07 &  ~~27.19 days \\
            & \XOOO & 448.37 &  119.14 days \\
            & \XOOX & 98.07 &  ~~~~1.49 years \\
            \hline\hline

            Metaphone &&& \\
            \hline
            & \OOOO & 27138.78 &  ~~~~1.97 days \\
            & \XOOO & 2822.74 &  ~~18.91 days \\
            & \XOOX & 339.84 &  157.45 days \\
            \hline\hline

            Levenshtein &&& \\
            \hline
            & \OOOO & 293.92 &  182.17 days \\
            & \XOOO & 102.75 &  ~~~~1.43 years \\
            & \XOOX & 35.53 &   ~~~~4.18 years \\
            \hline\hline

@@

        \begin{tabular}{|lll|}
            \hline
            \textbf{Attack Type} & \textbf{Metric} & \textbf{Vulnerable \%} \\
            \hline 
            \XOOX~(152) && \\ 
            & Levenshtein & ~~4.295\% \\
            & Metaphone & 24.095\% \\
            & NYSIIS & 10.441\% \\
            \hline\hline
            \XOOO~(1525) && \\ 
            & Levenshtein & ~~0.827\% \\
            & Metaphone & 15.569\% \\
            & NYSIIS & ~~4.341\% \\
            \hline\hline
            \OOOO~(15250) && \\ 
            & Levenshtein & ~~0.157\% \\
            & Metaphone & 10.202\% \\
            & NYSIIS & ~~1.824\% \\
            \hline\hline
        \end{tabular}
    }
    \caption{Number of vulnerable keys per metric}
    \label{tab:vulnkeys}
\end{table}

Table \ref{tab:vulnkeys} contains the breakdown of the number of vulnerable keys. The takeaways from this table are the extremely low values for Levenshtein in the higher attacks. This phenomenon is due to the low number of overall matches produced by Levenshtein, meaning the metric is not effective in the vast majority of cases. However, the standout metric is Metaphone with a sizeable proportion of vulnerable keys; it was the worst performer when assessed against real users but only by as little as 2\%. If you take into consideration, the number of vulnerable keys detected in the set alongside the average amount of near-collision matches in Table \ref{tab:average_perm} Metaphone appears to be the most usable metric overall.

\section{Generation of keys}
\label{sec:key_gen}
In order to demonstrate that the generation of the near-collision keys is not only theoretical, the actual generation was performed using GreenOnion. A random metric was selected from the three carried forward from the first experiment. Alongside this, a random uncontrolled key was generated as the simulated attack target (See Appendix \ref{appendix:uncontrolled_key} for the armor public key). Then for each attack level (\OOOO, \XOOO, \XOOX), a key was computed. NYSIIS was chosen as the selected metric. To expedite the process, an initial search was performed for controlled keys that had the highest number of near-collisions; this was due to the demonstrative purpose of this experiment. Producing near-matching keys from key pairs with a very small number of potential matches adds very little to this demonstration. This, however, will result in best-case scenario key computation times.

@@

    \makebox[\textwidth][c]{
        \begin{tabular}{|l|l|}
            \hline
            Potential near-collision keys & 142,296 \\
            Hashing speed & 4000 MH/s \\
            Estimated computation time & 9 hours \\
            Actual computation & 6.41 hours \\
            GPU Days & 0.52 \\
            \hline
            Original Trustwords & BELL GRIND ALGERIA ANNULI \\
            Actual Trustwords   & BOIL GRAND ALGER ANNUL \\
            \hline
        \end{tabular}
    }
    \caption{NYSIIS - OOOO}
    \label{tab:nysiis0}

    \makebox[\textwidth][c]{    
        \begin{tabular}{|l|l|}
            \hline
            Potential near-collision keys & 133,200 \\
            Hashing speed & 8000 MH/s \\
            Estimated computation time & 4.2 hours \\
            Actual computation & 5.12 hours \\
            GPU Days & 0.853 \\
            \hline
            Original Trustwords & ASSUMING SONOMA DENS KEENER \\
            Actual Trustwords   & ASSUMING SUMMON DENNI CONNOR \\
            \hline
        \end{tabular}
    }
    \caption{NYSIIS - XOOO}
    \label{tab:nysiis1}

    \makebox[\textwidth][c]{
        \begin{tabular}{|l|l|}
            \hline
            Potential near-collision keys & 16,464 \\
            Hashing speed & 6000 MH/s \\
            Estimated computation time & 2.16 days \\
            Actual computation & 23.44 hours \\
            GPU Days & 2.93 \\
            \hline
            Original Trustwords & VOCATION BORE TANN ANTE \\
            Actual Trustwords   & VOCATION BARE TONE ANTE \\
            \hline
        \end{tabular}
    }
    \caption{NYSIIS - XOOX}
    \label{tab:nysiis2}
\end{table}

@@

As can be seen most notably from Table \ref{tab:nysiis2}, the generation of the actual Trustwords differs in only 3 characters making it arguably very similar. When linking this generated key to results of the second experiment (See Section \ref{sec:exp2}) computation of 2.53 days on a single mid-range GPU can achieve around a 28\% success rate when assessed against actual users. Even with the least restricted attack type presented in Table \ref{tab:nysiis0}, the computation of half a day can provide almost a 10\% success rate when attacking users. This results in any user with a single commodity GPU could compute enough keys in less than a week to have a very high probability of deceiving an actual user.

### 2019-08-30 Writeup/Thesis/chapters/implementation.tex
Changes; - Re-drafted after reading over a printed version

Figure \ref{fig:increment} contains the code used to increment the exponent. Due to the exponent being split across two words alongside the limited functionality of OpenCL, bitwise operations to increment the exponent. The code utilises the fact that anything XORed with itself becomes zero alongside the fact that XORing a value $a$ with zero provides the result equal to $a$. The code manipulates the position of values by multiplication or division  of base-16 values; these shift the hex value either left or right, respectively. Once it is in position the "Mask" is created by XORing with the original value and the new intended value, this stores the changes required to reach the required values, this then applied to each of the words.
The \verb|get_global_id| command takes the ID from the currently running thread; this allows a different value to be used for each exponent concurrently

@@

Figure \ref{fig:matchExample} further shows the code used in the \verb|leven_similar|. The levenshtein difference is computed and compared to the tolerance discussed in Section \ref{sec:matches}. If this function returns true the match is added to the list of matches.

@@

In order to collate data for results later in the process, the state had to be retained. One potential solution would be to format the data and save it as a .csv file. However, this is a static way of data persistence and would require alteration every time the data schema was modified. The chosen solution utilised a python object serialisation library known as `Pickle'\footnote{\url{https://docs.python.org/2/library/pickle.html}}. This library saves the instance of a class as a file. This file then can be used to load the instance of the class back into the program. This inclusion allows changes to the object to filter down through the program and keeps the design of the application fluid. For example, after initial feedback gathered about the application, it was decided that the inclusion of `Round times' would be a useful addition. Edits were made to the \verb|experiment| class and the changes propagated through the application; no changes were needed on the save functionality. To distinguish between old and new save formats, a version number was used.

>>>>

Figure \ref{fig:increment} contains the code used to increment the exponent. Due to the exponent being split across two words alongside the limited functionality of OpenCL, bitwise operations are used to increment the exponent. The code utilises the fact that anything XORed with itself becomes zero alongside the fact that XORing a value $a$ with zero provides the result equal to $a$. The code manipulates the position of values by multiplication or division  of base-16 values; these shift the hex value either left or right, respectively. Once it is in position the "Mask" is created by XORing with the original value and the new intended value, this stores the changes required to reach the required values, this then applied to each of the words.
The \verb|get_global_id| command takes the ID from the currently running thread; this allows a different value to be used for each exponent concurrently

@@

Figure \ref{fig:matchExample} further shows the code used in the \verb|leven_similar|. The levenshtein difference is computed and compared to the tolerance discussed in Section \ref{sec:matches}. If this function returns true the match is added to the list.

@@

In order to collate data for results later in the process, the state had to be retained. One potential solution would be to format the data and save it as a \verb|.csv| file. However, this is a static way of data persistence and would require alteration every time the data schema was modified. The chosen solution utilised a python object serialisation library known as `Pickle'\footnote{\url{https://docs.python.org/2/library/pickle.html}}. This library saves the instance of a class as a file. This file then can be used to load the instance of the class back into the program. This inclusion allows changes to the object to filter down through the program and keeps the design of the application fluid. For example, after initial feedback gathered about the application, it was decided that the inclusion of `Round times' would be a useful addition. Edits were made to the \verb|experiment| class and the changes propagated through the application; no changes were needed on the save functionality. To distinguish between old and new save formats, a version number was used.

### 2019-08-30 Writeup/Thesis/chapters/introduction.tex
Changes; - Re-drafted after reading over a printed version

One proposed user-friendly scheme is Pretty Easy Privacy's (p$\equiv$p) "Trustwords". Trustwords is an implementation of word fingerprint mapping with a emphasis on usability. This increase in usability is achieved by the user comparing a reduced number of words. This usability boost, however, comes at a cost of a much larger word list.

>>>>

One proposed scheme claiming increased usability is Pretty Easy Privacy's (p$\equiv$p) "Trustwords". Trustwords is an implementation of word fingerprint mapping. This claimed increase in usability is achieved by the user comparing a reduced number of words compared to alternatives. This potential usability boost, however, comes at a cost of a much larger word list.
